QALY Comparison - Living Wage Intervention

### 2024-03-13 docsrc/documentation/notebooks/physical_activity.Rmd

---
title: "Housing"
output: html_document
bibliography: 
  - "docsrc/refs.bib"  # switch bibliography position. depending on where the file is being run. stick to this one when compiiling the website using the makefile
  #- "../../refs.bib" # use this one if knitting directly in Rstudio. Easier for debugging.
---

@@

## Housing Quality

Number of cigarettes consumed is an indicator of XXXX. test reference [@1987:nelson].

@@

```{r housing_barchart, echo=FALSE}
discrete_barplot("data/transitions/housing_quality/clm/housing_quality_2018_2019.rds", 'next_housing_quality')
```

@@

```{r housing_output, echo=FALSE}
options(width=120)
clm_barplot("data/transitions/housing_quality/clm/housing_quality_2018_2019.rds", "next_housing_quality") 
clm_output("data/transitions/housing_quality/clm/housing_quality_2018_2019.rds")
```

>>>>

---
title: "Physical Activity"
output: html_document
bibliography: 
  - "docsrc/refs.bib"  # switch bibliography position. depending on where the file is being run. stick to this one when compiiling the website using the makefile
  #- "../../refs.bib" # use this one if knitting directly in Rstudio. Easier for debugging.
---

@@

## Physical Activity

Whether a person is physically active or not has strong links to both mental and physical wellbeing, as well as other variables included in the MINOS pathways.

@@

```{r housing_barchart, echo=FALSE}
discrete_barplot("data/transitions/active/logit/active_2018_2019.rds", 'next_active')
```

@@

```{r active_output, echo=FALSE}
options(width=120)
clm_barplot("data/transitions/active/logit/active_2018_2019.rds", "next_active") 
clm_output("data/transitions/active/logit/active_2018_2019.rds")
```

### 2024-03-13 minos/outcomes/QALY_comparison.Rmd

---
title: "QALY Comparisons - Energy Crisis Interventions - NoSupport Baseline"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    df_print: paged
    code_folding: hide
params: 
  experiment: experiment 
  baseline: baseline 
  intervention: intervention
  intervention_label: intervention_label
---

>>>>

---
title: "QALY Comparisons - Energy Crisis Interventions - NoSupport Baseline"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    df_print: paged
    code_folding: hide
params: 
  experiment:
    value: experiment 
  baseline:
    value: baseline 
  intervention:
    value: intervention
  intervention_label:
    value: intervention_label
---

### 2024-03-13 minos/outcomes/QALY_comparison2.Rmd

ggplot(combined.diff, aes(x = year, y = total_boost, group = scenario, fill = scenario, color = scenario)) +
  geom_smooth() +
  labs(title = 'Total Boost amount by year') +
  scale_y_continuous(label = comma)
# 
# ggplot(combined, aes(x = year, y = alive_ratio, group = intervention, colour = intervention)) +
#   geom_smooth() +
#   labs(title = 'Ratio of living to dead in output dataframe')
# 
# ## incidence of mortality
# deaths <- combined %>%
#   select(run_id, intervention, year, alive_pop, dead_pop) %>%
#   group_by(run_id, intervention) %>%
#   mutate(total_pop = alive_pop + dead_pop,
#          deaths_this_year = dead_pop - lag(dead_pop)) %>%
#   group_by(run_id, year, intervention) %>%
#   summarise(death_incidence = deaths_this_year / total_pop)
# 
# ggplot(deaths, aes(x = year, y = death_incidence, group = intervention, colour = intervention)) +
#   geom_smooth() +
#   labs(title = 'Incidence of Mortality Comparison')
```

>>>>

ggplot(combined.diff, aes(x = year, y = total_boost, group = scenario, color = scenario)) +
  geom_smooth() +
  labs(title = 'Total Boost amount by year') +
  scale_y_continuous(label = comma)
# 
# ggplot(combined, aes(x = year, y = alive_ratio, group = intervention, colour = intervention)) +
#   geom_smooth() +
#   labs(title = 'Ratio of living to dead in output dataframe')
# 
# ## incidence of mortality
# deaths <- combined %>%
#   select(run_id, intervention, year, alive_pop, dead_pop) %>%
#   group_by(run_id, intervention) %>%
#   mutate(total_pop = alive_pop + dead_pop,
#          deaths_this_year = dead_pop - lag(dead_pop)) %>%
#   group_by(run_id, year, intervention) %>%
#   summarise(death_incidence = deaths_this_year / total_pop)
# 
# ggplot(deaths, aes(x = year, y = death_incidence, group = intervention, colour = intervention)) +
#   geom_smooth() +
#   labs(title = 'Incidence of Mortality Comparison')
```

### 2024-03-13 minos/testing/QALY_comparison_livingWage.Rmd

```{r}
# # read in QALY files for baseline and interventions
#out.path <- here::here('output', 'default_config')
#out.path <- here::here('output', 'glasgow_scaled')
out.path <- here::here('output', 'SF12_uk_scaled')

>>>>

```{r}
# # read in QALY files for baseline and interventions
out.path <- here::here('output', 'default_config')
#out.path <- here::here('output', 'glasgow_scaled')
#out.path <- here::here('output', 'SF12_uk_scaled')
